Hydraulically-vulnerable trees are buffered by deep-water access in a tropical forest community

### 2020-10-25 old_ms_sections.Rmd
1. moved extra isotopic data description

>>>>

Briefly, this isotopic approach makes use of a naturally formed gradient in deuterium to hydrogen ratio of soil water vertically belowground, which is generally formed due to evaporative enrichment (here, during the dry season). Shallow soil water has a greater deuterium to hydrogen content than deep soil water (here, $\mathrm{\delta}$^2^H~soil~ ranged from -16.5 to -50 ‰ over the depth of 0.5-1 m), with ground-water having the lowest deuterium to hydrogen content (here, -60 ‰), typically reflecting un-fractionated rain water. As root water-uptake is generally a non-fractionating process, $\mathrm{\delta}$^2^H~xylem~ of a tree reflects the signature of the source water. Thus water-sourcing depth of the tree can be identified as the depth with the same value of $\mathrm{\delta}$^2^H~soil~, or as that of $\mathrm{\delta}$^2^H~xylem~, with the uncertainty that the value of $\mathrm{\delta}$^2^H~xylem~ may also result from a mixing of water from shallower or deeper depths .
